Composition-climate paper

### 2015-06-20 Composition_Ecology.Rmd
Minor text changes.  Changes at head of Rmd to reflect changes in the sourced files.
Sourced files are now run as functions, keeping local variables internal so we don't have so many variables loaded globally.

Removed `R/load_fia.R` and put the function into `R/load_veg.R`.

source('R/Setup_R.R')
source('R/load_climate.R') # gives then.clim & now.clim
source('R/load_veg.R')
source('R/natural_earth.R')

@@

Mean temperatures in the region show an average increase of `r round(changes[3], 2)`^o^C since the 1895-1925 normal.  Annual precipitation has increased slightly (`r round(changes[1], 0)`mm), and maximum annual temeprature has declined slightly (`r round(changes[2], 2`^o^C)).  The most significant change has been in annual minimum temperatures, which have increased by `r round(changes[4], 1)` since the 1895-1925 normal.  This broad scale increase in winter temperatures is widely accepted, and results in an overall shift in the winter 'climate space' for the region.

>>>>

source('R/Setup_R.R')
source('R/load_climate.R') # gives then.clim & now.clim
source('R/load_veg.R')

pls_data <- get_pls('0.9-4')
agg_dens <- get_fia()[,colnames(pls_data)]

source('R/natural_earth.R')

base_map <- natural_earth()

@@

Mean temperatures in the region show an average increase of `r round(changes[3], 2)`^o^C since the 1895-1925 normal.  Annual precipitation has increased slightly (`r round(changes[1], 0)`mm), and maximum annual temeprature has declined slightly (`r round(changes[2], 2)`^o^C)).  The most significant change has been in annual minimum temperatures, which have increased by `r round(changes[4], 1)` since the 1895-1925 normal.  This broad scale increase in winter temperatures is widely accepted, and results in an overall shift in the winter 'climate space' for the region.
